Bioverse: Origins of Life

### 2023-11-03 src/tex/ms.tex
new plot with lum, NUV flux interpolations
describe interpolations

\subsection{H3: Life only originates on planets with particular UV irradiance}
Our third theoretical experiment is to test the UV irradiance requirement (Sect.~\ref{sec:predictions:uv}) by relating the occurrence of life on an exo-earth candidate with a minimum past quiescent stellar UV flux, focusing on the prebiotically interesting \gls{NUV} range from \SIrange{200}{280}{\nano\meter}. \todo[inline]{SUKRIT: got a good reference for this?}  %~\citep{RanjanSasselov2016}.?
Our concrete hypothesis shall be that life only occurs on planets that at some point in their history have received such radiation exceeded a minimum flux $F_\mathrm{NUV, min}$.
We further require this flux to have lasted for a minimum duration $\Delta T_\mathrm{min}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}, and the planet to be within its momentary \gls{HZ} during this entire period.

For each exo-earth candidate, we interpolated the age- and stellar mass-dependent \gls{NUV} fluxes in the \gls{HZ} obtained by \citet{Richey-Yowell2023} and computed the evolution of the inner (runaway greenhouse) and outer (maximum greenhouse) edges as a function of planet mass, stellar spectral type using the results of \citet{Kopparapu2014} and the stellar luminosity evolution of \citet{Baraffe1998}.
We then determined which planets were both in the \gls{HZ} and had \gls{NUV} fluxes above $F_\mathrm{NUV, min}$ for $\Delta T_\mathrm{min} \geq \var{deltaT_min}\,\SI{}{\mega\year}$.
We assigned the development of life to a fraction $f_\mathrm{life}$ of all temperate planets fulfilling these requirements.
For a population-level hypothesis, we then have
\begin{equation}\label{eq:hypothesis-uv}
    H_{3} = f_\mathrm{life} (\theta, F_\mathrm{NUV}) =
        \begin{cases}
            0 , & F_\mathrm{NUV} < F_\mathrm{NUV, min}\\
            f_\mathrm{life}, & F_\mathrm{NUV} \geq F_\mathrm{NUV, min} \,\mathrm{and\, in\, HZ} \, \mathrm{for} \, \Delta t \geq \var{deltaT_min} \,\SI{}{\mega\year}
        \end{cases}
\end{equation}
and the corresponding null hypothesis
%\begin{equation}
$H_{3, null} = f_\mathrm{life} (\theta),$
%\end{equation}
i.e., no correlation with UV flux.

@@

\subsubsection{past UV flux}
\todo[inline]{\citet{Günther2020} relate U-band energy to bolometric flux.}

\todo[inline]{OPTIONAL: ``We further test the scenario of a linear correlation of past UV flux and biosignature occurrence rate.
This test requires the detection of multiple biosignatures.''
~\\
Test for negative correlations as well?}

>>>>

\subsection{H3: Life only originates on planets with particular UV irradiance}
\todo[inline]{\citet{Guenther2020} relate U-band energy to bolometric flux.}
\todo[inline]{OPTIONAL: ``We further test the scenario of a linear correlation of past UV flux and biosignature occurrence rate.
This test requires the detection of multiple biosignatures.''
~\\
Test for negative correlations as well?}
Our third theoretical experiment is to test the UV irradiance requirement (Sect.~\ref{sec:predictions:uv}) by relating the occurrence of life on an exo-earth candidate with a minimum past quiescent stellar UV flux, focusing on the prebiotically interesting \gls{NUV} range from \SIrange{200}{280}{\nano\meter}. \todo[inline]{SUKRIT: got a good reference for this?}  %~\citep{RanjanSasselov2016}.?
Our concrete hypothesis shall be that life only occurs on planets that at some point in their history have received such radiation exceeded a minimum flux $F_\mathrm{NUV, min}$.
We further require this flux to have lasted for a minimum duration $\Delta T_\mathrm{min}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}, and the planet to be within its momentary \gls{HZ} during this entire period.

To determine \gls{HZ} occupancy, we interpolated the stellar luminosity evolution grid of \citet{Baraffe1998} using a Clough Tocher interpolant~\citep[][see left panel of Fig.~\ref{fig:hz_nuv_evo}]{Nielson1983,Alfeld1984} to compute the evolution of the inner (runaway greenhouse) and outer (maximum greenhouse) edges as a function of planet mass and stellar spectral type~\citep{Kopparapu2014}.
This provides each planet's epochs within and outside the \gls{HZ}.
For the \gls{NUV} flux, we use the age- and stellar mass-dependent \gls{NUV} fluxes in the \gls{HZ} obtained by \citet{Richey-Yowell2023}.
We linearly interpolate in their measured grid, where we convert spectral type to stellar mass using the midpoints of their mass ranges (\SI{0.75}{\Msun} for K~stars, \SI{0.475}{\Msun} for early-type M~stars,  and \SI{0.215}}{\Msun} for late-type M~stars).
Outside of the age and stellar mass range covered in \citet{Richey-Yowell2023}, we extrapolate using nearest simplex (see right panel of Fig.~\ref{fig:hz_nuv_evo}).

We then determined which planets were both in the \gls{HZ} and had \gls{NUV} fluxes above $F_\mathrm{NUV, min}$ for $\Delta T_\mathrm{min} \geq \var{deltaT_min}\,\SI{}{\mega\year}$.
We assigned the development of life to a random fraction $f_\mathrm{life}$ of all temperate planets fulfilling these requirements.
For a population-level hypothesis, we then have
\begin{equation}\label{eq:hypothesis-uv}
    H_{3} = f_\mathrm{life} (\theta, F_\mathrm{NUV}) =
        \begin{cases}
            0 , & F_\mathrm{NUV} < F_\mathrm{NUV, min}\\
            f_\mathrm{life}, & F_\mathrm{NUV} \geq F_\mathrm{NUV, min} \,\mathrm{and\, in\, HZ} \, \mathrm{for} \, \Delta t \geq \var{deltaT_min} \,\SI{}{\mega\year}
        \end{cases}
\end{equation}
and the corresponding null hypothesis
%\begin{equation}
$H_{3, null} = f_\mathrm{life} (\theta),$
%\end{equation}
i.e., no correlation with UV flux.

@@

\begin{figure*}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/hz_nuv_evo.pdf}
        \caption{Stellar luminosity evolution (left) and evolution of the \gls{NUV} flux in the \gls{HZ} as a function of host star mass. White markers show age and host star mass of the transiting planets in the synthetic sample.}
        \label{fig:hz_nuv_evo}
    \end{centering}
\end{figure*}
